Adolescent well-being in the digital age

### 2022-04-08 00-clean.Rmd
Add HDI cleaning

# Add regions to data tables
itu <- left_join(itu, regions)
gbd <- left_join(gbd, regions)
gwp <- left_join(gwp, regions)
# Remove now unnecessary variables
rm(no_region_gbd, no_region_gwp, regions_filled, regions)
```

@@

```{r}
write_rds(dat, "data/data-all.rds")
write_rds(itu, "data/itu.rds")
write_rds(gwp, "data/gwp.rds")
write_rds(gbd, "data/gbd.rds")
```

>>>>

# Add regions to data tables
itu <- left_join(itu, regions)
gbd <- left_join(gbd, regions)
gwp <- left_join(gwp, regions)
hdi <- left_join(hdi, regions) %>% 
  drop_na(region)

# Remove now unnecessary variables
rm(no_region_gbd, no_region_gwp, regions_filled, regions)
```

@@

```{r}
write_rds(dat, "data/data-all.rds")
write_rds(itu, "data/itu.rds")
write_rds(gwp, "data/gwp.rds")
write_rds(gbd, "data/gbd.rds")
write_rds(hdi, "data/hdi.rds")
```
